---
title: "A `xtable` Table: Output as HTML"
author: "Student R. Me"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
    html_document:
        keep_md: true
    pdf_document: default
    word_document: default
---


<!-- set root directory here --> 
<!-- your directory will be specific to you -->
```{r global_options, include=FALSE}
knitr::opts_knit$set(root.dir = "~/words/github/useRfiles/rmd-files")
knitr::opts_chunk$set(warning=FALSE)
```

---

---

## Data for table construction

```{r}
# import data and examine dataframe characteristics
  f1 <- read.csv("data/ospreypreybysex.csv", header = T)
  f1
```

---

## Default table using the package `xtable`

Note the default return is **.html** code.

```{r}
library(xtable)
print(xtable(f1), type ="html")
```

By adding the option `results="asis"` to the **chunk** the table is now rendered into text.

```{r, results="asis"}
library(xtable)
# xtable(f1)  NOT RUN: would return a default table of LaTex code
print(xtable(f1), type = "html", include.rownames = F)  # rendered table in html format
```

---

### The RMD code used to build the HTML output is in the box below

    ---
    title: "A `xtable` Table: Output as HTML"
    author: "Student R. Me"
    date: "`r knitr::inline_expr("format(Sys.time(), '%d %B, %Y')")`"
    html_document:
        keep_md: true
    pdf_document: default
    word_document: default 
    ---
    
    
    <!-- set root directory here --> 
    <!-- your directory will be specific to you -->
    ```{r global_options, include=FALSE}`r ''`
    knitr::opts_knit$set(root.dir = "~/words/github/useRfiles/rmd-files")
    knitr::opts_chunk$set(warning=FALSE)
    ```
    
    ---
    
    ---
    
    ## Data for table construction
    
    ```{r}`r ''`
    # import data and examine dataframe characteristics
      f1 <- read.csv("data/ospreypreybysex.csv", header = T)
      f1
    ```
    
    ---
    
    ## Default table using the package `xtable`
    
    Note the default return is **.html** code.
    
    ```{r}`r ''`
    library(xtable)
    print(xtable(f1), type ="html")
    ```
    By adding the option `results="asis"` to the **chunk** the table is now rendered into text.

    ```{r, results="asis"}`r ''`
    library(xtable)
    # xtable(f1)  NOT RUN: would return a default table of LaTex code
    print(xtable(f1), type = "html", include.rownames = F)  # rendered table in html format
    ```
    
    ---

