---
title: "Embedding and Executing Code"
author: "Student R. Me"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
    html_document:
        keep_md: true
    pdf_document: default
    word_document: default
---

---

## Running code

```{r iris_sum}
# some data analysis
summary(iris)
```

## Including Plots

```{r iris_plot}
# embed a plot
plot(iris$Sepal.Length)
```

---


### The RMarkdown .rmd code used to build the HTML output is in the box below

    ---
    title: "Embedding and Executing Code"
    author: "Student R. Me"
    date: "`r knitr::inline_expr("format(Sys.time(), '%d %B, %Y')")`"
    html_document:
        keep_md: true
    pdf_document: default
    word_document: default  
    ---
    
    ---
    
    ## Running code
    
    ```{r iris_sum}`r ''`
    # some data analysis
    summary(iris)
    ```
    
    ## Including Plots
    
    ```{r iris_plot}`r ''`
    # embed a plot
    plot(iris$Sepal.Length)
    ```
    
    NOTE that both chunks have been named, iris_sum and iris_plot, respectively.  
    Naming chunks can be useful for debugging purposes.
    
    ---
